---
title: "Example | Slender-billed Curlew"
format: 
  html:
    toc: true
    code-fold: true
    embed-resources: true
editor: visual
execute: 
  warning: false
lightbox: true  
---

# Setup

Install `dodo` (if needed):

```{r install-dodo, output=FALSE}
renv::install("Louis-Backstrom/dodo")
```

```{r dodo-version}
cat("Using dodo version", as.character(packageVersion("dodo")))
```

Load libraries:

```{r load-libraries}
library(dodo)
library(tidyverse)
library(readxl)
library(countrycode)
library(rgbif)
library(future)
library(furrr)
library(ggh4x)
```

Get models:

```{r get-models}
models <- read_xlsx("EDE Models.xlsx", range = "B2:R50") %>%
  fill(everything(), .direction = "down") %>%
  filter(`dodo?` == "✓") %>%
  pull(ID)
```

Set up parallel processing:

```{r setup-parallel}
plan(multisession, workers = floor(parallel::detectCores() * 0.5))
# plan(sequential)
```

Set key parameters:

```{r overwrite}
overwrite <- FALSE
```

```{r parameters}
alpha <- 0.05

init_time <- 1817 # Original description
last_time <- 2022 # End of Buchanan et al. dataset
curr_time <- 2026 # Current year

certainty_threshold <- 0.9
```

Set up functions for models:

```{r model-functions}
run_model <- function(model, records, surveys, effort, alpha, test_time) {
  out <- switch(model,
    "SL88F1" = SL88F1(records = records$ccon, alpha = alpha),
    "SS89F1" = SS89F1(records = records$ccon, alpha = alpha),
    "SS89B1" = SS89B1(
      records = records$ccon, alpha = alpha, length.out = 1e5,
      scale = 0.01
    ),
    "SO93F1" = SO93F1(
      records = records$ccon, alpha = alpha, init.time = init_time,
      test.time = test_time
    ),
    "SO93B1" = SO93B1(
      records = records$ccon, init.time = init_time,
      test.time = test_time, pi = 0.5
    ),
    "SO93F2" = SO93F2(
      records = records$ccon, alpha = alpha, init.time = init_time,
      test.time = test_time, precBits = 1024
    ),
    "MA94F1" = MA94F1(records = records$ccon, alpha = alpha, gamma = 0.5),
    "BU95F1" = BU95F1(records = records$cdis),
    "BU95F2" = BU95F2(records = records$cdis),
    "BU95F3" = BU95F3(records = records$cdis),
    "MA97F1" = MA97F1(
      records = records$cdis, effort = effort, alpha = alpha,
      init.time = init_time
    ),
    "MC98F1" = MC98F1(records = records$cdis, effort = effort),
    "MC99F1" = MC99F1(
      records = records$ccon, alpha = alpha,
      test.time = test_time
    ),
    "WM99B1" = WM99B1(
      records = records$cbin, surveys = init_time:test_time,
      alpha = alpha, test.time = test_time, priors = list(
        lambda = 1e3, c = 1, d = 1
      ), increment = 0.01
    ),
    "RS03F1" = RS03F1(
      records = records$ccon, alpha = alpha,
      conf.int = "one-sided", k = ifelse(length(
        records$ccon
      ) >= 10, 10, length(records$ccon)),
      test.time = test_time
    ),
    "SR03F1" = SR03F1(
      records = records$ccon, alpha = alpha,
      test.time = test_time
    ),
    "MC06F1" = MC06F1(records = records$cbin, alpha = alpha, init.time = init_time),
    "RO09B1" = RO09B1(
      records = records$cbin, pi = 0.5, n.chains = 4,
      n.iter = 11e4, n.burnin = 1e4
    ),
    "JE10F1" = JE10F1(
      records = records$ccon, alpha = alpha, init.time = init_time,
      test.time = test_time
    ),
    "JE10F2" = JE10F2(
      records = records$ccon, alpha = alpha, init.time = init_time,
      test.time = test_time
    ),
    "BR12F1" = BR12F1(records = records$ccon, alpha = alpha),
    "SO12B1" = SO12B1(
      records = records$ubin, init.time = init_time, increment = 0.001,
      gamma = 1, record.check = "error"
    ),
    "TH13B1" = TH13B1(
      records = records$umcb,
      priors = list(
        p = setNames(
          replicate(length(grep(
            "^records_", names(records$umcb)
          )), 0.5, simplify = FALSE),
          paste0("p", seq_len(length(grep("^records_", names(records$umcb)))))
        ),
        q = setNames(
          lapply(as.numeric(sub("^records_", "", grep(
            "^records_", names(records$umcb),
            value = TRUE
          ))), function(x) {
            if (x >= certainty_threshold) 1 else 0.5
          }),
          paste0("q", seq_len(length(grep("^records_", names(records$umcb)))))
        )
      ),
      certain = which(as.numeric(sub("^records_", "", grep("^records_", names(
        records$umcb
      ), value = TRUE))) >= certainty_threshold),
      PXT = NULL, PE = NULL
    ),
    "TH13B2" = TH13B2(
      records = records$umcb,
      priors = list(
        p = setNames(
          replicate(length(grep(
            "^records_", names(records$umcb)
          )), c(0, 1), simplify = FALSE),
          paste0("p", seq_len(length(grep("^records_", names(records$umcb)))))
        ),
        q = setNames(
          lapply(as.numeric(sub("^records_", "", grep(
            "^records_", names(records$umcb),
            value = TRUE
          ))), function(x) {
            if (x >= certainty_threshold) c(1, 1) else c(0, 1)
          }),
          paste0("q", seq_len(length(grep("^records_", names(records$umcb)))))
        )
      ),
      certain = which(as.numeric(sub("^records_", "", grep("^records_", names(
        records$umcb
      ), value = TRUE))) >= certainty_threshold),
      PXT = NULL, PE = NULL, n.iter = 10e4, pb = FALSE
    ),
    "TH13B3" = TH13B3(
      records = records$umcb,
      priors = list(
        p = setNames(
          replicate(length(grep(
            "^records_", names(records$umcb)
          )), c(0, 1), simplify = FALSE),
          paste0("p", seq_len(length(grep("^records_", names(records$umcb)))))
        ),
        q = setNames(
          lapply(as.numeric(sub("^records_", "", grep(
            "^records_", names(records$umcb),
            value = TRUE
          ))), function(x) {
            if (x >= certainty_threshold) c(1, 1) else c(0, 1)
          }),
          paste0("q", seq_len(length(grep("^records_", names(records$umcb)))))
        )
      ),
      certain = which(as.numeric(sub("^records_", "", grep("^records_", names(
        records$umcb
      ), value = TRUE))) >= certainty_threshold),
      PXT = NULL, PE = NULL, n.iter = 10e4, pb = FALSE
    ),
    "AL14B1" = AL14B1(records = records$cbin),
    "CB14B1" = CB14B1(
      records = records$cbin, alpha = alpha, init.time = init_time,
      test.time = test_time, n.iter = 10e4
    ),
    "CB14B2" = CB14B2(
      records = records$cbin, alpha = alpha, init.time = init_time,
      test.time = test_time, burn.in = 1e4, n.iter = 11e4
    ),
    "JR14F1" = JR14F1(
      records = records$ucon, alpha = alpha, init.time = init_time,
      test.time = test_time
    ),
    "LE14B1" = LE14B1(
      records = records$iucn, surveys = surveys,
      threshold = certainty_threshold, prior = c(0, 1), n.iter = 10e4
    ),
    "LE14B2" = LE14B2(
      records = records$ubin, alpha = alpha, init.time = init_time,
      n.chains = 4, n.iter = 11e4, n.burnin = 1e4, n.thin = 10
    ),
    "SB14B1" = SB14B1(records = records$ubin, init.time = init_time, increment = 0.001),
    "SB14B2" = SB14B2(records = records$ubin, init.time = init_time, increment = 0.001),
    "AL15B1" = AL15B1(records = records$cbin),
    "SO16B1" = SO16B1(
      records = records$cbin, init.time = NULL,
      test.time = NULL, curr.time = NULL
    ),
    "SO16B2" = SO16B2(
      records = records$cbin, init.time = NULL,
      test.time = NULL, curr.time = NULL
    ),
    "WA16B1" = WA16B1(
      records = records$ccon, alpha = alpha, init.time = init_time
    ),
    "TH17I1" = TH17I1(records = records$iucn, surveys = surveys),
    "BR19F1" = BR19F1(
      records = records$ucon, alpha = alpha, init.time = init_time,
      test.time = test_time, n.iter = 10e4
    ),
    "BR19F2" = BR19F2(
      records = records$ucon, alpha = alpha, init.time = init_time,
      test.time = test_time, n.iter = 10e4
    ),
    "BR19F3" = BR19F3(
      records = records$ucon, alpha = alpha, init.time = init_time,
      test.time = test_time, n.iter = 10e4
    ),
    "BR19F4" = BR19F4(
      records = records$ucon, alpha = alpha, init.time = init_time,
      test.time = test_time, n.iter = 10e4
    ),
    "BR19F5" = BR19F5(
      records = records$ucon, alpha = alpha, init.time = init_time,
      test.time = test_time, n.iter = 10e4
    ),
    "TH19B1" = TH19B1(
      records = records$iucn, surveys = surveys,
      init.time = max(records$ccon) + 1, test.time = test_time,
      pi = 0.5
    ),
    "KO20B1" = KO20B1(
      records = records$cbin, alpha = alpha, init.time = init_time,
      test.time = test_time, n.chains = 4, n.iter = 11e4,
      n.burnin = 1e4, n.thin = 10
    ),
    "KO20B2" = KO20B2(
      records = records$ubin, alpha = alpha, init.time = init_time,
      test.time = test_time, record.check = "remove",
      n.chains = 4, n.iter = 11e4, n.burnin = 1e4, n.thin = 10
    ),
    "KO21B1" = KO21B1(
      records = records$ubin, alpha = alpha, init.time = init_time,
      test.time = test_time, n.chains = 4, n.iter = 11e4,
      n.burnin = 1e4, n.thin = 10
    ),
  )

  if (is.null(out)) {
    stop("Unknown model name: ", model)
  }

  return(out)
}

test_model <- function(model, output, alpha, test_time) {
  out <- switch(model,
    "SL88F1" = output$conf.int[2] < test_time,
    "SS89F1" = output$conf.int[2] < test_time,
    "SS89B1" = output$cred.int[2] < test_time,
    "SO93F1" = output$p.value < alpha,
    "SO93B1" = output$p.extant < alpha,
    "SO93F2" = output$p.value < alpha,
    "MA94F1" = output$conf.int[3] < test_time,
    "BU95F1" = output$p.value < alpha,
    "BU95F2" = output$p.value < alpha,
    "BU95F3" = output$p.value < alpha,
    "MA97F1" = output$conf.int[2] < test_time,
    "MC98F1" = output$p.value < alpha,
    "MC99F1" = output$p.value < alpha,
    "WM99B1" = output$p.extant < alpha,
    "RS03F1" = output$p.value < alpha,
    "SR03F1" = output$p.value < alpha,
    "MC06F1" = output$p.value < alpha,
    "RO09B1" = output$p.extant < alpha,
    "JE10F1" = output$p.value < alpha,
    "JE10F2" = output$p.value < alpha,
    "BR12F1" = output$estimate < test_time,
    "SO12B1" = output$Bayes.factor > (1 / alpha),
    "TH13B1" = output$p.extant < alpha,
    "TH13B2" = output$p.extant < alpha,
    "TH13B3" = output$p.extant < alpha,
    "AL14B1" = output$p.extant < alpha,
    "CB14B1" = output$p.extant < alpha,
    "CB14B2" = output$p.extant < alpha,
    "JR14F1" = output$p.value < alpha,
    "LE14B1" = output$p.extant < alpha,
    "LE14B2" = output$p.extant < alpha,
    "SB14B1" = output$Bayes.factor > (1 / alpha),
    "SB14B2" = output$Bayes.factor > (1 / alpha),
    "AL15B1" = output$p.extant < alpha,
    "SO16B1" = output$p.extant < alpha,
    "SO16B2" = output$p.extant < alpha,
    "WA16B1" = output$cred.int[2] < test_time,
    "TH17I1" = output$p.extant < alpha,
    "BR19F1" = output$p.extant < alpha,
    "BR19F2" = output$p.extant < alpha,
    "BR19F3" = output$p.extant < alpha,
    "BR19F4" = output$p.extant < alpha,
    "BR19F5" = output$p.extant < alpha,
    "TH19B1" = output$p.extant < alpha,
    "KO20B1" = output$p.extant < alpha,
    "KO20B2" = output$p.extant < alpha,
    "KO21B1" = output$p.extant < alpha,
  )

  if (is.null(out)) {
    stop("Unknown model name: ", model)
  }

  return(out)
}
```

Set up output directory:

```{r directory}
dir.create(file.path("Outputs", "Slender-billed Curlew"),
  recursive = TRUE,
  showWarnings = FALSE
)
```

# Data

Read in and process records datasheet from Buchanan et al.:

```{r records}
records_raw <- read_xlsx("Data/Slender-billed Curlew.xlsx",
  sheet = 1, range = "A1:F1175"
) %>%
  select(
    year = "Year",
    country = "Country",
    locality = "Locality",
    p_ci_min = "P(CI) Lower",
    p_ci = "P(CI) Est",
    p_ci_max = "P(CI) Upper"
  ) %>%
  filter(
    year >= init_time,
    year <= last_time
  ) %>%
  as.data.frame()

lost_time <- records_raw %>%
  filter(
    p_ci >= certainty_threshold, # Confirmed records
  ) %>%
  pull(year) %>%
  max()

test_times <- lost_time:curr_time
grid <- expand.grid(test_time = test_times)

records_full <- convert_dodo(records_raw,
  init.time = init_time, test.time = curr_time,
  threshold = certainty_threshold, unique = TRUE,
  aggregate = "max", time = "year", certainty = "p_ci",
  certainty_lower = "p_ci_min", certainty_upper = "p_ci_max"
)
```

Read in and process survey datasheet:

```{r surveys}
surveys_raw_active <- read_xlsx("Data/Slender-billed Curlew.xlsx",
  sheet = 2, range = "A1:J16"
) %>%
  mutate(survey = TRUE) %>%
  select(
    time = "Year",
    survey = "survey",
    epsilon = "EPS Est",
    epsilon_lower = "EPS Lower",
    epsilon_upper = "EPS Upper",
    p_i = "PI Est",
    p_i_lower = "PI Lower",
    p_i_upper = "PI Upper",
    p_r = "PR Est",
    p_r_lower = "PR Lower",
    p_r_upper = "PR Upper"
  )

surveys_raw_passive <- read_xlsx("Data/Slender-billed Curlew.xlsx",
  sheet = 2, range = "O1:X2"
) %>%
  mutate(survey = FALSE) %>%
  select(
    survey = "survey",
    epsilon = "EPS Est",
    epsilon_lower = "EPS Lower",
    epsilon_upper = "EPS Upper",
    p_i = "PI Est",
    p_i_lower = "PI Lower",
    p_i_upper = "PI Upper",
    p_r = "PR Est",
    p_r_lower = "PR Lower",
    p_r_upper = "PR Upper"
  ) %>%
  expand_grid(
    tibble(time = init_time:curr_time) %>%
      filter_out(time %in% surveys_raw_active$time),
    .
  )

surveys_full <- bind_rows(surveys_raw_active, surveys_raw_passive) %>%
  arrange(time) %>%
  as.data.frame()
```

Create or read in effort proxy:

```{r effort, message=FALSE, warning=FALSE}
core_countries <- records_raw %>%
  filter(p_ci >= certainty_threshold) %>%
  group_by(country) %>%
  tally() %>%
  filter(n > 5) %>%
  pull(country) %>%
  sort() %>%
  countrycode(., origin = "country.name", destination = "iso2c")

if (!file.exists("Outputs/Slender-billed Curlew/effort_full.rds") | overwrite) {
  effort_raw <- tibble(
    year = integer(),
    country = character(),
    species = character()
  )

  for (country in core_countries) {
    for (year in init_time:curr_time) {
      species_list <- occ_search(
        taxonKey = 212, # Birds
        country = country,
        year = year,
        facet = "speciesKey",
        facetLimit = 10000,
        limit = 0 # Just get facets, no occurrences
      )$facets$speciesKey$name

      species_list <- tibble(
        year = year,
        country = country,
        species = species_list
      )

      effort_raw <- bind_rows(effort_raw, species_list)

      Sys.sleep(0.1)
    }
  }

  effort_full <- effort_raw %>%
    drop_na(species) %>%
    group_by(year) %>%
    summarise(n_species = n_distinct(species)) %>%
    left_join(tibble(year = init_time:curr_time), ., by = "year") %>%
    mutate(n_species = replace_na(n_species, 0)) %>%
    pull(n_species)
} else {
  effort_full <- readRDS("Outputs/Slender-billed Curlew/effort_full.rds")
}
```

Save full processed datasets:

```{r save-data}
saveRDS(records_full, "Outputs/Slender-billed Curlew/records_full.rds")
saveRDS(surveys_full, "Outputs/Slender-billed Curlew/surveys_full.rds")
saveRDS(effort_full, "Outputs/Slender-billed Curlew/effort_full.rds")
```

# Run

```{r}
set.seed(1234)
```

Run models:

```{r run-models}
if (file.exists("Outputs/Slender-billed Curlew/model_times.rds")) {
  model_times <- readRDS("Outputs/Slender-billed Curlew/model_times.rds")
} else {
  model_times <- tibble(
    model = character(), run_time = numeric(),
    end_time = POSIXct()
  )
}

for (model in models) {
  model_start <- Sys.time()
  model_ran <- FALSE

  model_file <- file.path("Outputs", "Slender-billed Curlew", paste0(model, ".rds"))

  valid_file <- FALSE
  if (file.exists(model_file)) {
    check <- readRDS(model_file)
    if (!is.null(check$results) && nrow(check$results) == nrow(grid)) {
      valid_file <- TRUE
    }
    rm(check)
  }

  if (!valid_file || overwrite == TRUE) {
    model_ran <- TRUE

    results <- future_map(seq_len(nrow(grid)), function(idx) {
      test_time <- grid$test_time[idx]

      records <- convert_dodo(records_raw,
        init.time = init_time,
        test.time = test_time, threshold = certainty_threshold, unique = TRUE,
        aggregate = "max", time = "year", certainty = "p_ci",
        certainty_lower = "p_ci_min", certainty_upper = "p_ci_max"
      )
      surveys <- surveys_full %>%
        filter(time <= test_time)
      effort <- effort_full[1:(test_time - init_time + 1)]

      iteration_start <- Sys.time()

      warning_msg <- character()
      error_msg <- NA_character_

      output <- tryCatch(
        withCallingHandlers(
          run_model(
            model = model, records = records, surveys = surveys,
            effort = effort, alpha = alpha, test_time = test_time
          ),
          warning = function(w) {
            warning_msg <<- c(warning_msg, conditionMessage(w))
            invokeRestart("muffleWarning")
          }
        ),
        error = function(e) {
          error_msg <<- conditionMessage(e)
          NULL
        }
      )

      i_time <- difftime(Sys.time(), iteration_start, units = "secs") %>%
        as.numeric()

      result <- if (is.null(output)) {
        tibble(
          model = model, test_time = test_time,
          last_time = max(records$ccon), isextinct = NA, output = NA,
          warning = length(warning_msg) > 0, error = TRUE,
          warning_msg = if (length(warning_msg) > 0) {
            paste(unique(warning_msg), collapse = " | ")
          } else {
            NA_character_
          },
          error_msg = if (length(error_msg) > 0) {
            paste(unique(error_msg), collapse = " | ")
          } else {
            NA_character_
          }, run_time = i_time, end_time = Sys.time()
        )
      } else {
        tibble(
          model = model, test_time = test_time,
          last_time = max(records$ccon), isextinct = test_model(
            model, output, alpha, test_time
          ), output = list(output),
          warning = length(warning_msg) > 0, error = FALSE,
          warning_msg = if (length(warning_msg) > 0) {
            paste(unique(warning_msg), collapse = " | ")
          } else {
            NA_character_
          },
          error_msg = NA_character_, run_time = i_time, end_time = Sys.time()
        )
      }

      rm(output)
      gc()

      return(result)
    }, .options = furrr_options(seed = TRUE))

    all_results <- bind_rows(results)

    saveRDS(list(model = model, results = all_results), model_file)
  }

  if (model_ran == TRUE) {
    m_time <- as.numeric(difftime(Sys.time(), model_start, units = "secs"))

    model_times <- model_times %>%
      filter(model != !!model) %>%
      bind_rows(tibble(
        model = model, run_time = m_time,
        end_time = Sys.time()
      ))
  }

  gc()
}

saveRDS(model_times, "Outputs/Slender-billed Curlew/model_times.rds")
```

# Finish

Results:

```{r results}
model_files <- list.files("Outputs/Slender-billed Curlew", pattern = "\\.rds$", full.names = TRUE)
model_files <- model_files[!grepl("model_times\\.rds$", model_files)]
model_files <- model_files[!grepl("records_full\\.rds$", model_files)]
model_files <- model_files[!grepl("surveys_full\\.rds$", model_files)]
model_files <- model_files[!grepl("effort_full\\.rds$", model_files)]

all_results <- map_dfr(model_files, function(model_file) {
  results_file <- readRDS(model_file)

  if (!is.null(results_file$results)) {
    results_file$results
  } else {
    warning("No results in ", basename(model_file))
    NULL
  }
})

model_times <- readRDS("Outputs/Slender-billed Curlew/model_times.rds")
total_time <- sum(model_times$run_time) / 60
cat(sprintf("Total model execution time: %.2f minutes\n", total_time))
```

# Runtime

```{r runtime}
#| fig-dpi: 300
#| fig-width: 8
#| fig-height: 4
ggplot(model_times) +
  geom_col(
    aes(x = factor(model, levels = models), y = run_time / 60)
  ) +
  labs(x = "Model", y = "Total Runtime (min)") +
  theme_bw() +
  theme(axis.text.x = element_text(
    angle = 90, vjust = 0.5, hjust = 1, family = "mono", face = "bold"
  ))
```

# Summary

```{r summary}
#| fig-dpi: 600
#| fig-width: 3
#| fig-height: 3
models <- read_xlsx("EDE Models.xlsx", range = "B2:R50") %>%
  fill(everything(), .direction = "down") %>%
  pull(ID)

all_results <- all_results %>%
  mutate(model = factor(model, levels = models))

excluded <- all_results %>%
  left_join(tibble(model = models), ., by = "model") %>%
  filter(is.na(isextinct)) %>%
  select(model) %>%
  unique() %>%
  mutate(model = factor(model, levels = models))

inc_results <- all_results %>%
  filter_out(model %in% excluded$model) %>%
  mutate(model = factor(model, levels = models))

cat("Excluded (NA outputs):", as.character(excluded$model))

summary_plot <- inc_results %>%
  group_by(test_time) %>%
  summarise(extinct_count = sum(isextinct, na.rm = TRUE)) %>%
  ggplot() +
  geom_point(aes(x = test_time, y = extinct_count)) +
  geom_line(aes(x = test_time, y = extinct_count), linewidth = 1) +
  geom_hline(
    yintercept = length(models) - nrow(excluded),
    linetype = "dashed"
  ) +
  theme_classic() +
  labs(
    x = "Test Time",
    y = "Models Inferring Extinction",
    title = "C) Slender-billed Curlew"
  )

saveRDS(summary_plot, "Outputs/Slender-billed Curlew/summary_plot.rds")
summary_plot

results_plot <- ggplot() +
  geom_point(
    data = inc_results,
    aes(x = test_time, y = as.integer(isextinct))
  ) +
  geom_line(
    data = inc_results,
    aes(x = test_time, y = as.integer(isextinct)), linewidth = 1
  ) +
  geom_label(
    data = excluded,
    label = "Excluded", x = (lost_time + curr_time) / 2,
    y = 0.5, fontface = "italic"
  ) +
  theme_classic() +
  theme(
    strip.background = element_blank(),
    strip.text = element_text(family = "mono", face = "bold")
  ) +
  labs(
    x = "Test Time",
    y = "Extinct (1) / Extant (0)"
  )
```

```{r summary-portrait}
#| fig-dpi: 600
#| fig-width: 9
#| fig-height: 12
results_plot +
  facet_wrap2(~model,
    drop = FALSE, ncol = 6, nrow = 8,
    axes = "all", remove_labels = "all"
  )
```

```{r summary-landscape}
#| fig-dpi: 600
#| fig-width: 12
#| fig-height: 6
results_plot +
  facet_wrap2(~model,
    drop = FALSE, ncol = 8, nrow = 6,
    axes = "all", remove_labels = "all"
  )
```

```{r summary-models}
last_extinct <- inc_results %>%
  filter(test_time == .env$last_time)

cat("Extinction inference at end of original dataset:")
last_extinct %>%
  group_by(isextinct) %>%
  tally()

curr_extinct <- inc_results %>%
  filter(test_time == max(test_time))

cat("Extinction inference in final year:")
curr_extinct %>%
  group_by(isextinct) %>%
  tally()

estimate_models <- read_xlsx("EDE Models.xlsx", range = "B2:R50") %>%
  fill(everything(), .direction = "down") %>%
  filter(
    ID %in% (curr_extinct %>%
      filter(isextinct == TRUE) %>%
      pull(model)),
    `Est.` == "✓"
  ) %>%
  pull(ID)

curr_estimate <- curr_extinct %>%
  filter(model %in% estimate_models, !is.na(isextinct)) %>%
  mutate(estimate = purrr::map(output, "estimate")) %>%
  pull(estimate) %>%
  as.numeric()

cat("Estimated extinction times:")
length(curr_estimate)
summary(curr_estimate)

interval_models <- read_xlsx("EDE Models.xlsx", range = "B2:R50") %>%
  fill(everything(), .direction = "down") %>%
  filter(
    ID %in% (curr_extinct %>%
      filter(isextinct == TRUE) %>%
      pull(model)),
    `Int.` == "✓"
  ) %>%
  pull(ID)

curr_interval <- curr_extinct %>%
  filter(model %in% interval_models, !is.na(isextinct)) %>%
  mutate(interval = purrr::map(output, ~ .x$cred.int %||% .x$conf.int)) %>%
  pull(interval) %>%
  purrr::map_dbl(2) %>%
  as.numeric()

cat("Estimated upper interval bounds:")
length(curr_interval)
summary(curr_interval)
```

# Errors, Warnings, etc.

```{r issues}
all_results %>%
  filter(is.na(warning_msg) == FALSE) %>%
  group_by(model, warning_msg) %>%
  tally() %>%
  print(n = Inf)

all_results %>%
  filter(is.na(error_msg) == FALSE) %>%
  group_by(model, error_msg) %>%
  tally() %>%
  print(n = Inf)
```
